---
title: "Initial Admeet Feedback Analysis"
output:
  html_notebook: default
  pdf_document: default
  html_document:
    df_print: paged
  word_document: default
---
The following is initial analysis for the feedback data of video calls being run in various collegiate prefrosh social groups, such as MIT, Harvard and Princeton. (Data collected by Admeet).

```{r}
setwd("~/Desktop/baseball/")
data <- read.csv(file = "AdmeetInit.csv")
print(head(data))
```
Initalizing the data and visualizing the first 6 rows using the head function.

```{r}
timestamp <- as.vector(data[,1])
email <- as.vector(data[,2])
sociability <- as.vector(data[,3])
final <- as.vector(data[,4])
time <- as.vector(data[,5])
topic <- as.vector(data[,6])
dominance <- as.vector(data[,7])
experience <- as.vector(data[,8])
name <- as.vector(data[,9])
```
Defining all of our columns of data as vectors - allowing for easiest future use of the variables.

```{r}
#prepping the data
sociability <- suppressWarnings(na.omit(sociability))
experience <- suppressWarnings(na.omit(experience))
#plotting the chart
plot(sociability, experience)
title(main = "User Experience based off of Sociability")
abline(lm(experience ~ sociability), col = "blue", lwd = 2)
#finding the regression 
fit = lm(experience ~ sociability)
summary(fit)
```
Based off of the chart, it seems introverts had marginally worse experiences on the video calls, which makes sense.
```{r}
#require("tm")
#require("ggplot2")
plot(final, experience)
title(main = "User Experience based off of Number of People in Group")
abline(lm(experience ~ final), col = "blue", lwd = 2)
#finding the regression 
fit = lm(experience ~ final)
summary(fit)
```
As more people joined the group, callers' experiences were incrementally boosted.
```{r}
require("gplots")
#dive into the previous data more - what is the best group size?
size_matrix = rbind(experience, final)
heatmap.2(size_matrix)
title(main = "Heatmap based off of Final # of Group members and Experience")
```



